---
title: "Alcohol vs Seat choice"
author: "Roselyn Villatoro"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question 
Is there a difference between the alcohol consumed between the row
you choose to sit in??

##Method
predict alcohol consumption base on where you sit

$H_0$: There is no difference between the alcohol consumed between the row you sit in. 

$H_A$: There is a difference between the alcohol consumed between the row you sit in.  

alcohol is numerical  
seat is categorical, so we use the Numerical~Cat helper file.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  The boxplot shows that the consumption of alcohol for those in the back seats is the highest, while those in the middle seats consumed less, but more than those you consumed the least in the front seats.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The average of ounces of alcohol consumed for those seated in the back would be 8.5, while those seated in the front have an average of 1.7 and those in the middle consumed and average of 3.3 ounces of alcohol.

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is 0.000116 which is lower than 0.05, which causes us to reject the null hypothesis.

```{r}
plot(TukeyHSD(model1))
```

The tukey shows that both front-back and middle-back are different, but middle-front is not different.

## Conclusions

The boxplot showed us that those in the back seat consumed the most amount of alcohol while those in the middle seats consumed less than them and those seated in the front consumed the least amount of alcohol. Then the numerical summary showed us how the average of ounces of alcohol consumed by the people in the back seats is 8.5, the average consumed by those in the front seats is 1.7 and finally those in the middle seats consumed and average of 3.3 ounces of alcohol.The p-value in inferential tests is 0.000116 which is lower than 0.05. We then reject the null hypothesis since there is a difference in alcohol consumption based on where you sit. 
